On Designing Collusion-Resistant Incentive Mechanisms for Mobile Crowdsensing Systems

### 2015-12-15 techreport.tex
Discuss the lower and upper bounds of the claimed cost units. Address the third item of Review 1.
Cite the prior distribution argument in Koutsopoulos's paper from INFOCOM'13.

{\color{blue} 
Note that in many practical applications, the total number of discrete sensing tasks is upper bounded \cite{Alt2010Location,Liu2013A,li2012location}. We also assume the payment sum is upper bounded by the budget $B$. To upper bound each $n_i$, we introduce $P_m$, the maximum payment to any user. Let $n$ be the number of participating users. Then we require $B\geq nP_m$. On the other hand, for each user, the assigned number of sensing tasks cannot exceed the number of remaining tasks to do. Otherwise, the platform will not allow the user to do any task. This is reflected by the threshold $R$, the number of remaining tasks in Algorithm \ref{alg:np}.
}

>>>>

{\color{blue} 
We assume for each user $i$, its cost unit $\kappa_i$ must fall in some publicly known interval $[\underline{\kappa}_i,\overline{\kappa}_i]$. The lower and upper bounds can be found by the historical distribution of claimed cost units from user $i$ \cite{koutsopoulos2013optimal}.

Note that in many practical applications, the total number of discrete sensing tasks is upper bounded \cite{Alt2010Location,Liu2013A,li2012location}. We also assume the payment sum is upper bounded by the budget $B$. To upper bound each $n_i$, we introduce $P_m$, the maximum payment to any user. Let $n$ be the number of participating users. Then we require $B\geq nP_m$. On the other hand, for each user, the assigned number of sensing tasks cannot exceed the number of remaining tasks to do. Otherwise, the platform will not allow the user to do any task. This is reflected by the threshold $R$, the number of remaining tasks in Algorithm \ref{alg:np}.
}
